### 2016-05-20 paper/paper.tex
Added new figure
Adding in-text reference
Adding some text in PAY_TO_DDoS

\section{DDoSCoin Design}

@@

Miners in DDoSCoin repeatedly create connections to a TLS victim server, and
check for a response that satisfies a target difficulty decided by the network.
If the response satisfies this condition, then parameters of the TLS handshake
can be published by the miner to create a new valid block.

@@

Although not yet implemented, the current TLS 1.3 proposal appears to also have the
necessary properties that enable DDoSCoin. In particular, the
Certificate Verify message includes a signature from the server over essentially
all prior handshake messages, including the Client Hello that contains the
\texttt{client\_random}. Thus, DDoSCoin could be used against TLS 1.3
servers with only minor modifications.

@@

where $txid$ is the transaction ID of the PAY\_TO\_DDOS transaction,
$output\_script$ is the SHA256 hash of the output script the payee wants to collect the
payment with, and $N$ is a 32-byte random nonce.  The client then makes connections to the
specified victim domain until it gets a response that meets the target
difficulty specified by the PAY\_TO\_DDOS transaction.
($SHA256(server\_key\_exchange\_params || signature || N) < target$).

@@

% Maybe move this to discussion....
Since PAY\_TO\_DDOS transactions can be claimed by anyone, there is a risk to
the collector that by the time they complete their DoS attack, someone else will
have collected the payment. In addition, a potential victim website could
disincentivize attacks by submitting PAY\_TO\_DDOS transactions that they can
quickly solve locally. This would cause attackers to try to connect to them, and
eventually even collect a response that meets the target difficulty. However,
when the attacker went to publish this to collect the reward, the victim could
publish their proof, essentially double-spending the PAY\_TO\_DDOS transaction.
With some probability, the victim's transaction will ``win'' and prevent the
attacker from collecting the reward. Over the long term, attackers may be wary
of attacking such targets, and instead require higher payouts for attacking them
to cover such risks.

>>>>

\section{DDoSCoin Design}
\FigTLS

@@

Miners in DDoSCoin repeatedly create connections to a TLS victim server, and
check for a response that satisfies a target difficulty decided by the network.
If the response satisfies this condition, then parameters of the TLS handshake
can be published by the miner to create a new valid block. This connection is
depicted in Figure~\ref{fig:tls-connection}.

@@

Although not yet implemented, the current TLS 1.3 proposal appears to also have the
necessary properties that enable DDoSCoin~\cite{tls-draft}. In particular, the
Certificate Verify message includes a signature from the server over essentially
all prior handshake messages, including the Client Hello that contains the
\texttt{client\_random}. Thus, DDoSCoin could be used against TLS 1.3
servers with only minor modifications.

@@

where $txid$ is the transaction ID of the PAY\_TO\_DDOS transaction,
$output\_script$ is the SHA256 hash of the output script the payee wants to collect the
payment with, and $N$ is a 32-byte random nonce.  The client then makes connections to the
specified victim domain until it gets a response that meets the target
difficulty specified by the PAY\_TO\_DDOS transaction, i.e. the hash of the key exchange 
parameters, signature, and nonce are less than the target hash value.

@@

% Maybe move this to discussion....

Since PAY\_TO\_DDOS transactions can be claimed by anyone, there is a risk to
the collector that by the time they complete their DoS attack, someone else will
have collected the payment. Any target specified by a PAY\_TO\_DDOS transaction
could use their priveleged position to turn the proof-of-work into a computational challenge.
Since the challenge is no longer bound by the network, the target can claim the reward for
themselves. Quickly solved PAY\_TO\_DDOS transactions with no degradation of service
would indicate to the actor providing the bounty that the target is claiming its own bounty.

In addition, a potential victim website could
disincentivize attacks by submitting PAY\_TO\_DDOS transactions that they can
quickly solve locally. This would cause attackers to try to connect to them, and
eventually even collect a response that meets the target difficulty. However,
when the attacker went to publish this to collect the reward, the victim could
publish their proof, essentially double-spending the PAY\_TO\_DDOS transaction.
With some probability, the victim's transaction will ``win'' and prevent the
attacker from collecting the reward. Over the long term, attackers may be wary
of attacking such targets, and instead require higher payouts for attacking them
to cover such risks.
